Unsupervised

### 2023-12-15 Unsupervised.Rmd
yuh

```{r}
distCirrhosis <- dist(
  x = cirrhosisCluster,
  method = "euclidean"
)

@@

StagesPalette <- c("#AA336A", "#770737", "#40B5AD", "#009E60")

@@

@@

```{r}
# Plot the final dendrogram for hybrid approach ----
# library(factoextra)
fviz_dend(
  x = hybridCirrhosis,
  cex = 0.4,
  palette = StagesPalette,
  rect = FALSE,
  horiz = TRUE,
  repel = TRUE,
  main = "Final Dendrogram"
)

@@

>>>>

## DO I NEED THIS DIST??
```{r}
distCirrhosis <- dist(
  x = cirrhosisCluster,
  method = "euclidean"
)

@@

StagesPalette <- c("#AA336A", "#770737", "#40B5AD", "#009E60", "#9FE2BF")

@@

```
### Testing for optimal k value

```{r}
# Create scree plot for choosing k ----
library(factoextra)
set.seed(380)
fviz_nbclust(
  x = cirrhosisCluster,
  diss = NULL,
  FUNcluster = kmeans,
  method = "wss",
  k.max = 10
)

@@

### Trying k = 5

hybridCirrhosis2 <- hkmeans(
  x = cirrhosisCluster,
  k = 5,
  hc.metric = "euclidean",
  hc.method = "ward.D",
  iter.max = 10
)

```{r}
# Plot the final dendrogram for hybrid approach ----
# library(factoextra)
fviz_dend(
  x = hybridCirrhosis2,
  cex = 0.4,
  palette = StagesPalette,
  rect = FALSE,
  horiz = TRUE,
  repel = TRUE,
  main = "Final Dendrogram"
)

@@

# Plot the final clustering for hybrid approach ----
# library(factoextra)
fviz_cluster(
  object = hybridCirrhosis2,
  stand = FALSE,
  geom = "point",
  main = "Hybrid Cluster Plot"
) +
  scale_color_manual(values = StagesPalette) +
  scale_fill_manual(values = StagesPalette) +
  theme_bw()
